Biomass and species richness temporal trends drives the assembly and the disassembly of food-web in natural fish assemblages

### 2021-06-16 paper/manuscript.Rmd
Add new figures and add std coef to results

In order to control for the uncertainties of the estimated temporal trends, each
temporal trend was weighted by the inverse of the product of the standard errors of the
estimated trends, i.e. slopes for the response and the explicative
variable.

@@

@@

Overall, we found high heterogeneity in the explicative power of statistical
models linking temporal dynamics of food-web structure and the one of community
biomass and species richness spanning from $R_{adj}^2= `r rsq_piel_nind`$ for
pielou of individual number to $R_{adj}^2= `r rsq_tlvl`$ for average trophic
level (Table \@ref(tab:rsq)). The spatial models
 were more performant, with $R_{cond}^2$ varing from 
`r rsq_tlvl_sp` to `r rsq_piel_bm_sp` (Table \@ref(tab:rsq-sp)).

@@

```{r}
loadd(model_log_bm_f3y_table_medium, model_log_rich_f3y_table_medium)
reg_bm <- model_log_bm_f3y_table_medium$reg_table
#reg_bm[reg_bm$y == ]
```
We found a significant positive relationship between the temporal trends of
community biomass from one side and species richness, average trophic level,
connectance from the other side (Fig. \@ref(fig:bm), Table \@ref(tab:aov)),
meaning that they temporally increased when the community biomass temporally increased and
respectively that they temporally decreased when the community biomass decreased in
time.

We found a significant negative relationship between the temporal trends of
community biomass and that of the pielou of biomass (Figure \@ref(fig:bm), Table
\@ref(tab:aov)), meaning that the eveness of biomass across species
temporally increased when the community biomass temporally decreased and
respectively that the evenness of biomass temporally decreased when the community biomass
temporally increased (Fig. \@ref(fig:bm), Table \@ref(tab:aov)). We also found the
same pattern between the temporal trends of community biomass and that of the
pielou of individual number.

@@

The temporal trends of community biomass and pielou of biomass, had a positive
relationship with that of species richness (Fig. \@ref(fig:rich), Table
\@ref(tab:aov)) while we did not find significant relationships between the
temporal trends of average trophic level, connectance, pielou of individual
number and the one of species richness (Fig. \@ref(fig:rich), Table
\@ref(tab:aov)).

@@

@@

We found that species richness, connectance, average trophic level were
spatially positively related to community biomass while the pielou of biomass
was negatively related to community biomass (Fig. \@ref(fig:bm), Table
\@ref(tab:aov-sp)). However, we found no spatial relation between the pielou of
individual and community biomass.

@@

We found that community biomass, the pielou of biomass and individual were
positively related to species richness while average trophic level and
connectance were negatively related to
community biomass (Fig. \@ref(fig:rich), Table \@ref(tab:aov-sp)).

@@

We found that the temporal increase of the average trophic level was positively
linked to increase of community biomass. Increase of average trophic level can
be associated to either gain of biomass in the highest trophic level nor losses
of biomass in the lowest trophic. In our case, such gain or losses of average
trophic level is probably associated to the variations of the presence of large
fishes. This interpretation is confirmed by the finding that the evenness of
biomass, measured by the pielou, decreased through time as community biomass
decrease and reversely, meaning that biomass distribution across species
respectively become respectively less and more even when community biomass
decrease and increase. We also found no relationship between the temporal trends of evenness based
on indivual number and that community biomass, confirming that the temporal trends
of community biomass in our study is linked to few big individuals. It further
indicates that temporal loss of community biomass are linked with the loss of
the higher trophic level.

@@

To the difference with community biomass, the temporal trends of evenness of
biomass and individual were positively related to the temporal trends of species
richness, meaning that as species richness temporally increase, the
distribution of biomass and abondance become more even. Our results indicate
that biomass trends are linked to few big individuals while richness trends are
linked to overall shift in dominance in communities.

Surprinsingly, we found the temporal trends of connectance was not related to
the one of species richness as found spatially in most empirical foodweb
[@dunne_network_2006] and also in the present study. This result suggests that
the structure of food-webs might be not very sensitive to variation of species
richness and that species loss and gain concerns species of low trophic level,
which in turn does not affect connectance. However, the relationship become
slightly negative for species poor communities. An explanation might be that
species-rich communities already contains a significant number of piscivores,
which have the most links whereas species poor communites contains few
piscivores.

@@

- Add loss of species richness, loss of biomass and increase dominance?

HERE
 @soininen_relationship_2012;

@@

We found that community biomass was linked positively related to species richness
both in space and in time, indicating that space for time might be use. In the
same way, we found a positive relationship between average trophic
level and community biomass both in time and in space. However, it was not the case
for connectance and average trophic level that were respectively weakly or not
linked to species richness in time whereas our result shows a strong negative
relation in space. Moreover, connectance displayed a strong positive
relationship with biomass in time but not in space. This result is in accordance
with other studies which found mismatch between spatial and temporal patterns
[@adler_contrasting_2007; @johnson_testing_2008]. This mismatch is mainly due to the crucial assumptions
that variations in space will correspond to differences of assembly stages and
then reflect the assembly/disassembly trajectories in time of communities [@].

@@

## Biomass and richness gains and losses are symmetric processes in terms of community structure

We found no case in which gain or losses of biomass and richness lead to
different relationship between the temporal dynamic of community structure and
the one of biomass and species richness. We could have imagined that
extinction/colonisation processes or immigration/extinction debt could have lead
to different relationships.

@@

We showed that BEF works in time but that richness and biomass temporal trends
through time relates on different ecological processes. We further found that
space for time subtitution does not always work.

@@

>>>>

In order to control for the uncertainties of the estimated temporal trends, each
temporal trend was weighted by the inverse of the product of the standard errors of the
estimated trends, i.e. slopes for the response and the explicative
variables.

@@

The significativity of the effects were tested with ANOVA.  In order to be able
to compare the magnitude of the effects of community biomass and species
richness in both temporal and spatial models, we computed standardized slopes
($r_{\delta}$) and their associated standard errors.

$r_{\delta} = \beta\frac{s_x}{s_y}$

with $\beta$ being the unstandardised slope, $s_x$ and $s_y$ the standard
deviation of the explicative and response variable.

All the statistical models displayed low multicollinearity (VIF < 3, Table XX).
We visually inspected the residuals of the linear models (TODO).

@@

Overall, we found high heterogeneity in the explicative power of statistical
models linking temporal dynamics of food-web structure and the one of community
biomass and species richness spanning from $R_{adj}^2= `r rsq_piel_nind`$ for
pielou of individual number to $R_{adj}^2= `r rsq_tlvl`$ for average trophic
level (Table \@ref(tab:rsq)). The spatial models were more performant, with
$R_{cond}^2$ varing from $`r rsq_tlvl_sp`$ to $`r rsq_piel_bm_sp`$ (Table
\@ref(tab:rsq-sp)).

@@

```{r}
loadd(std_table_bm_rich_mono_stable_trends)
std <-
  std_table_bm_rich_mono_stable_trends %>%
  mutate(
    type = recode(type, spatial = "sp", temporal = "tps"),
    response = recode(response, log_bm_std = "bm", log_rich_std = "rich", ct_ff
      = "ct", piel_bm = "p_bm", piel_nind = "p_n", w_trph_lvl_avg = "tlvl"),
    term = recode(term, log_bm_std = "bm", log_rich_std = "rich")
    ) %>%
  rename(t = type, rep = response, sest = std_estimate) %>%
  mutate_at(vars(sest, stdse), ~round(.x, 2))
tps_bm <- std %>%
  filter(t == "tps", term == "bm")

tps_bm_sest <- tps_bm$sest
names(tps_bm_sest) <- tps_bm$rep
```
We found a significant positive relationship between the temporal trends of
community biomass from one side and species richness, average trophic level,
connectance from the other side (Fig. \@ref(fig:bm), Table \@ref(tab:aov),
respectively  $r_\delta = `r tps_bm_sest["rich"]`$, $`r tps_bm_sest["tlvl"]`$, 
$`r tps_bm_sest["ct"]`$), meaning that they temporally increased when the community
biomass temporally increased and respectively that they temporally decreased
when the community biomass decreased in time.

We found a significant negative relationship between the temporal trends of
community biomass and that of the pielou of biomass 
( $r_\delta = `r tps_bm_sest["p_bm"]`$), meaning that the eveness of biomass
across species
temporally increased when the community biomass
temporally decreased and respectively that the evenness of biomass temporally
decreased when the community biomass temporally increased (Fig. \@ref(fig:bm),
Table \@ref(tab:aov)). We also found the same pattern between the temporal
trends of community biomass and that of the pielou of individual number
($r_\delta = `r tps_bm_sest["p_n"]`$).

@@

```{r}
tps_r <- std %>%
  filter(t == "tps", term == "rich")

tps_r_sest <- tps_r$sest
names(tps_r_sest) <- tps_r$rep
```

The temporal trends of community biomass and pielou of biomass, had a positive
relationship with that of species richness (Fig. \@ref(fig:rich), Table
\@ref(tab:aov), $r_\delta = `r tps_r_sest["p_bm"]`$) while we did not find
significant relationships between the temporal trends of average trophic level,
connectance, pielou of individual number and the one of species richness (Fig.
\@ref(fig:rich), Table \@ref(tab:aov)).

@@

```{r}
sp_b <- std %>%
  filter(t == "sp", term == "bm")
sp_b_sest <- sp_b$sest
names(sp_b_sest) <- sp_b$rep

sp_r <- std %>%
  filter(t == "sp", term == "rich")
sp_r_sest <- sp_r$sest
names(sp_r_sest) <- sp_r$rep
```

@@

We found that species richness, connectance, average trophic level were
spatially positively related to community biomass (resp. 
$r_\delta = `r sp_b_sest["rich"]`$, $`r sp_b_sest["ct"]`$, 
$`r sp_b_sest["tlvl"]`$, Fig.
\@ref(fig:bm), Table \@ref(tab:aov-sp)) while the pielou of biomass was
negatively related to community biomass ($r_\delta = `r sp_b_sest["p_bm"]`$).
However, we found no spatial relation between the pielou of individual and
community biomass.

@@

Community biomass, the pielou of biomass and individual were
positively related to species richness (resp. 
$r_\delta = `r sp_r_sest["bm"]`$, $`r sp_r_sest["p_bm"]`$,
$`r sp_r_sest["p_n"]`$) while average
trophic level and connectance were negatively related to
species richness (resp. $r_\delta = `r sp_r_sest["tlvl"]`$, $`r sp_r_sest["ct"]`$,
Fig. \@ref(fig:rich), Table \@ref(tab:aov-sp)).

@@

We found that the temporal increase of the average trophic level was positively
linked to increase of community biomass in line with a previous model suggesting
that the presence of higher predator can lead to higher community biomass
[@wang_biodiversity_2018]. Increase of average trophic level can be associated
to either gain of biomass in the highest trophic level nor losses of biomass in
the lowest trophic. In our case, such gain or losses of average trophic level is
probably associated to the variations of the presence of large fishes. The
finding that the evenness of biomass, measured by the pielou, decreased through
time as community biomass decrease and reversely, meaning that biomass
distribution across species respectively become respectively less and more even
when community biomass decrease and increase. We also found that evenness
decreased temporally of number of individual when community biomass increased
temporally, confirming that the temporal trends of community biomass in our
study is linked to big individuals. It further indicates that temporal loss of
community biomass are linked with the loss of the higher trophic level.

@@

To the difference with community biomass, the temporal trends of eveness of
biomass was positively related to the temporal trends of species
richness, meaning that as species richness temporally increase, the
distribution of biomass become more even, while temporal trends of eveness of
individual had no significant relationship with species richness. Those results
indicate that biomass trends are linked to few big individuals while richness
trends are linked to overall shift in dominance in communities.

Surprinsingly, we found that the temporal trends of connectance was not related to
the one of species richness as found spatially in most empirical food-web
[@dunne_network_2006] and also in the present study. This result suggests that
the structure of food-webs might be not very sensitive to variation of species
richness and that species loss and gain concerns species of low trophic level,
which in turn does affect connectance very little. However, the relationship become
slightly negative for species poor communities. An explanation might be that
species-rich communities already contains a significant number of piscivores,
which have the most links whereas species poor communites contains few
piscivores.

@@

@@

While space for time works for variation of community biomass, it is less clear
for the variation of species richness. Indeed, it was not the case for
connectance and average trophic level that were respectively weakly or not
linked to species richness in time whereas our result shows a strong negative
relation in space. This result is in line with other studies which found
mismatch between spatial and temporal patterns [@adler_contrasting_2007;
@johnson_testing_2008]. This mismatch is mainly due to the crucial assumptions
that variations in space will correspond to differences of assembly stages and
then reflect the assembly/disassembly trajectories in time of communities [@].

In contrast with a meta-analysis [@soininen_relationship_2012], we found that
the eveness of individual number is positively related to the one of species
richness in space in stream fish assemblages but found no relationship in time.

@@

---
### Biomass and richness gains and losses are symmetric processes in terms of community structure
#
#We found no case in which gain or losses of biomass and richness lead to
#different relationship between the temporal dynamic of community structure and
#the one of biomass and species richness. We could have imagined that
#extinction/colonisation processes or immigration/extinction debt could have lead
to different relationships.
---

@@

Our study shows that richness and biomass temporal trends in natural fish
communities relate on different ecological processes, biomass temporal dynamics
being related to variation of highest trophic level while it is not the case for
species richness. Our work also suggests that space for time substitution may be
relevant to predict food-web community structure in case of biomass variation
but not for species richness variation. We look forward to next investigations
to see the generality of assembly rules in food-webs. There are crucial to
better understand the temporal dynamics of food-webs structure and then its
impact on ecosystem functioning.

@@

```{r}
std_cap <- paste0(
  "Standardized coefficients of the effects of community biomass and species
  richness on food-web structure for the temporal and spatial models. The lines
  display the standard errors."
)
```

```{r std, fig.cap=std_cap}
loadd(fig_std_coef)
fig_std_coef
```
